Modal type theory based on the intuitionistic epistemic logic

### 2018-02-09 article.tex
modified

Where $\mathbb{V}^{*}$ and $\Lambda_{{\bf K}}^{*}$ denote the set of finite sequences of variables $\bigcup \limits_{i=0}^{\infty} \mathbb{V}_i$
and the set of finite sequences of terms $\bigcup \limits_{i = 0}^{\infty} {\Lambda_{{\bf K}}}_i $. Note that the sequence of variables $\vec{x}$ and the sequence of terms $\vec{M}$ should have the same length.
Otherwise, term is not well-formed.

>>>>

Where $\mathbb{V}^{*}$ and $\Lambda_{{\bf K}}^{*}$ denote the set of finite sequences of variables $\bigcup \limits_{i=0}^{\infty} \mathbb{V}^i$
and the set of finite sequences of terms $\bigcup \limits_{i = 0}^{\infty} {\Lambda_{{\bf K}}}^i $. Note that the sequence of variables $\vec{x}$ and the sequence of terms $\vec{M}$ should have the same length.
Otherwise, term is not well-formed.
